On the Design, Implementation and Use of Laziness in R

### 2019-09-05 report/paper.Rmd
Fix graph margins to prevent labels from getting cut and fix labels

argument_promise_count_by_value_type <-
    argument_promise_count_by_value_type %>%
    filter(type!="Unbound" ,type!="Function Call", type!="...", type!="Builtin", type!="Bytecode") %>%
    filter(type!="Expression", type!="Externalptr", type!="Special", type!="Unknown (Jumped)") %>%
    filter(type!="Pairlist", type!="Missing", type!="Weakref")

@@

argument_promise_count_by_expression_type_graph <-
    argument_promise_count_by_expression_type %>%
    ggplot(aes(reorder(type, -count),
               relative_promise_count)) +
    geom_col(fill="grey45") + coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    theme(legend.title = element_blank(),
          legend.position = "top")

@@

argument_promise_count_by_value_lookup_count_graph <-
    argument_promise_count_by_value_lookup_count %>%
    filter(value_lookup_count %in% c(0:6, ">=7")) %>%
    ggplot(aes(value_lookup_count, relative_promise_count)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    scale_x_discrete(limits = c(0:6, ">=7"))

@@

```{r, eval=TRUE, echo=FALSE}
## convert evaluation time to seconds from milliseconds
## so that the scale can format it to appropriate time units
execution_time_graph <-
    execution_times %>%
    mutate(execution_time = log10(execution_time / 1000)) %>%
    ggplot(aes(lookup_class, execution_time,
               color = lookup_class,
               weight = relative_argument_count)) +
    geom_violin() + 
    coord_flip() + 
    theme(legend.position = "none") +
    scale_y_continuous(labels = function(x) { time_labels(10 ^ x) }) +
    labs(x = "", y = "")

@@

```{r,eval=TRUE,echo=FALSE}
call_by_escape_and_type <- 
    call_by_escape_and_type %>%
    rename(type=return_value_type) %>%
    filter(!(type %in% c("Unbound", "...", "Builtin", "Bytecode",
                         "Expression", "Externalptr", "Special", "Unknown (Jumped)",
                         "Pairlist", "Missing", "Weakref", "Promise", "S4", "Raw", "Complex")))
type_order <-
    call_by_escape_and_type %>%
    filter(category == "Escaped") %>%
    arrange(desc(relative_call_count)) %>%
    pull(type)

@@

force_order_graph <-
    force_orders %>%
    filter(type == "compatible") %>%
    filter(force_order_count %in%  c(2:5, "> 5")) %>%
    arrange(force_order_count) %>%
    ggplot(aes(x = force_order_count, y = relative_function_count)) +
    geom_col() + 
    scale_x_discrete(limits = c(2:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_function_count, labels=count_labels),
                       labels = relative_labels) +
    coord_flip() +
    labs(x = "", y = "")

@@

argument_promise_call_depth_graph <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth %in% c(1:5, "> 5")) %>%
    ggplot(aes(call_depth, relative_promise_count)) +
    geom_col() +
    scale_x_discrete(limits = c(1:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
                                           labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip()

>>>>

argument_promise_count_by_value_type <-
    argument_promise_count_by_value_type %>%
    filter(type!="Unbound" ,type!="Function Call", type!="...", type!="Builtin", type!="Bytecode") %>%
    filter(type!="Expression", type!="Externalptr", type!="Special", type!="Unknown (Jumped)") %>%
    filter(type!="Pairlist", type!="Missing", type!="Weakref") %>%
    filter(type!="Promise")

@@

argument_promise_count_by_expression_type_graph <-
    argument_promise_count_by_expression_type %>%
    ggplot(aes(reorder(type, -count),
               relative_promise_count)) +
    geom_col(fill="grey45") + coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count, labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") +
    theme(legend.title = element_blank(),
          legend.position = "top",
          plot.margin = margin(r=10))

@@

argument_promise_count_by_value_lookup_count_graph <-
    argument_promise_count_by_value_lookup_count %>%
    filter(value_lookup_count %in% c(0:6, ">=7")) %>%
    mutate(value_lookup_count = replace(value_lookup_count, value_lookup_count == ">=7", "> 6")) %>%
    ggplot(aes(value_lookup_count, relative_promise_count)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    scale_x_discrete(limits = c(0:6, "> 6"))

@@

```{r, eval=TRUE, echo=FALSE}
## convert evaluation time to seconds from milliseconds
## so that the scale can format it to appropriate time units
execution_time_graph <-
    execution_times %>%
    mutate(execution_time = log10(execution_time / 1000)) %>%
    ggplot(aes(lookup_class, execution_time,
               color = lookup_class,
               weight = relative_argument_count)) +
    geom_violin() + 
    coord_flip() + 
    theme(legend.position = "none",
          plot.margin = margin(r=20)) +
    scale_y_continuous(labels = function(x) { time_labels(10 ^ x) }) +
    labs(x = "", y = "")

@@

```{r,eval=TRUE,echo=FALSE}
call_by_escape_and_type <- 
    call_by_escape_and_type %>%
    rename(type=return_value_type) %>%
    filter(!(type %in% c("Unbound", "...", "Builtin", "Bytecode",
                         "Expression", "Externalptr", "Special", "Unknown (Jumped)",
                         "Pairlist", "Missing", "Weakref", "Promise", "Raw", "Complex")))
type_order <-
    call_by_escape_and_type %>%
    filter(category == "Escaped") %>%
    arrange(desc(relative_call_count)) %>%
    pull(type)

@@

force_order_graph <-
    force_orders %>%
    filter(type == "compatible") %>%
    filter(force_order_count %in%  c(2:5, "> 5")) %>%
    arrange(force_order_count) %>%
    ggplot(aes(x = force_order_count, y = relative_function_count)) +
    geom_col() + 
    scale_x_discrete(limits = c(2:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_function_count, labels=count_labels),
                       labels = relative_labels) +
    coord_flip() +
    labs(x = "", y = "") +
    theme(plot.margin = margin(r=10))

@@

argument_promise_call_depth_graph <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth %in% c(0:5, "> 5")) %>%
    mutate(call_depth = if_else(call_depth == "0", "1",
                        if_else(call_depth == "1", "2",
                        if_else(call_depth == "2", "3",
                        if_else(call_depth == "3", "4",
                        if_else(call_depth == "4", "5",
                        if_else(call_depth == "5", "6",
                        if_else(call_depth == "> 5", "> 6", "?")))))))) %>%
    ggplot(aes(call_depth, relative_promise_count)) +
    geom_col() +
    scale_x_discrete(limits = c(1:6, "> 6")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
                                           labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip()
